---
title: "Hw4"
output: html_document
---

Problem 1: Bicycling World Problem
a.
```{r message=FALSE}
Model = c('Fierro 7B', 'HX 5000', 'Durbin Ultralight', 'Schmidt', 'WSilton Advanced', 'bicyclette velo', 'Supremo Team', 'XYC Racer', 'DOnofrio Pro', 'Americana #6')
Weight = c(17.9, 16.2, 15.0, 16.0, 17.3, 13.2, 16.3, 17.2, 17.7, 14.2)
Price = c(2200, 6350, 8470, 6300, 4100, 8700, 6100, 2680, 3500, 8100)
df <- data.frame(Model, Weight, Price)
plot(Weight, Price, main="Scatterplot", xlab="Bicycles Weight", ylab="Price")
```

b.
```{r message=FALSE}
model1 = lm(df$Price ~ df$Weight)
model1$coefficients
```
y = b0 + b1*x = 28818 - 1439*x

c.
```{r message=FALSE}
summary(model1)
```
H0: beta0 = 0, Ha: beta0 != 0, p-value = 9.99e-05, p-value < 0.05, so slope is significant to the model
H0: beta1 = 0, Ha: beta1 != 0, p-value = 2.15e-05, p-value < 0.05, so intercept is significant to the model

d.
R-squared = 0.8637, so 86.37% of the variation in the prices of the bicycles is accounted for the weight of bicycles.


Problem 2: Assembly Line Problem
a.
```{r message=FALSE}
LineSpeed = c(20,20,40,30,60,40)
numberofdefectivepart = c(21,19,15,16,14,17)
df2 = data.frame(LineSpeed, numberofdefectivepart)
plot(LineSpeed, numberofdefectivepart, main="Scatterplot2", xlab="Line Speed", ylab="Number of Defective Parts Found")
```
The number of defective parts found is decrease as the line speed increase.

b.
```{r message=FALSE}
model2 = lm(df2$numberofdefectivepart ~ df2$LineSpeed)
summary(model2)
```
y = b0 + b1*x = 22.1739 - 0.1478*x

c.
H0: beta0 = 0, Ha: beta0 != 0, p-value = 0.000179, p-value < 0.01, so slope is significant to the model
H0: beta1 = 0, Ha: beta1 != 0, p-value = 0.028135, p-value < 0.01, so intercept is insignificant to the model

d.
R-squared = 0.7391, so 73.91% of the variation in the number of defective part is accounted for the line speed.


Problem 3: Jensen Tire & Auto Problem
a.
```{r message=FALSE}
WeeklyUsage = c(13,10,20,28,32,17,24,31,40,38)
AMexpense = c(17,22,30,37,47,30.5,32.5,39,51.5,40)
df3 = data.frame(WeeklyUsage, AMexpense)
plot(WeeklyUsage, AMexpense, main="Scatterplot3", xlab="Weekly Usage Hours", ylab="Annual Maintenance Expense")
```
Annual Maintenance Expense is positively related to Weekly Usage Hours

b.
```{r message=FALSE}
model3 = lm(df3$AMexpense ~ df3$WeeklyUsage)
summary(model3)
```
y = b0 + b1*x = 10.5280 + 0.9534*x


4.Toyota Problem
a.
```{r message=FALSE}
Miles = c(22,29,36,47,63,77,73,87,92,101,110,28,59,68,68,91,42,65,110)
Price = c(16.2,16,13.8,11.5,12.5,12.9,11.2,13,11.8,10.8,8.3,12.5,11.1,15,12.2,13,15.6,12.7,8.3)
df4 = data.frame(Miles, Price)
plot(Miles, Price, main="Scatterplot4", xlab="Miles", ylab="Price")
```

b.
```{r message=FALSE}
model4 = lm(df4$Price ~ df4$Miles)
summary(model4)
```
y = b0 + b1*x = 16.46976 − 0.05878*x

c.
H0: beta0 = 0, Ha: beta0 != 0, p-value = 0.000348, p-value < 0.01, so slope is significant to the model
H0: beta1 = 0, Ha: beta1 != 0, p-value = 2.99e-12, p-value < 0.01, so intercept is significant to the model

d.
R-squared = 0.5387, so 53.87% of the variation in the price of the car is accounted for the miles of the car.

e.
```{r message=FALSE}
predict(model4)
head(sort(residuals(model4)),2)
```

f.
```{r message=FALSE}
16.4698-0.0587*60
```


5. Dodger Stadium Attendance
Q1:
a.
```{r message=FALSE}
url = "https://raw.githubusercontent.com/jcbonilla/BusinessAnalytics/master/BAData/dodgers.csv"
Dodger = read.csv(url)
df5 = as.data.frame(Dodger)
table(df5$cap)
table(df5$shirt)
table(df5$bobblehead)
table(df5$fireworks)
```

b.
```{r message=FALSE}
by(data = df5$attend, INDICES = df5$cap, FUN = mean)
by(data = df5$attend, INDICES = df5$shirt, FUN = mean)
by(data = df5$attend, INDICES = df5$bobblehead, FUN = mean)
by(data = df5$attend, INDICES = df5$fireworks, FUN = mean)
```

c.
```{r message=FALSE}
by(data = df5$attend, INDICES = df5$day_of_week, FUN = mean)
by(data = df5$attend, INDICES = df5$month, FUN = mean)
by(data = df5$attend, INDICES = df5$skies, FUN = mean)
by(data = df5$attend, INDICES = df5$day_night, FUN = mean)
```

d.
```{r message=FALSE}
library(ggplot2)
library(dplyr)
p = ggplot(df5, aes(x=reorder(opponent, -attend), y=attend)) + stat_summary(fun.y="mean", geom="bar")
p + geom_hline(yintercept=mean(df5$attend), linetype="dashed", color = "red")
```

Q2:
a.
```{r message=FALSE}
model5 = lm(df5$attend ~ df5$bobblehead + df5$fireworks + df5$shirt + df5$cap)
summary(model5)
```
Bobblehead promotions will increase attendance.

b. Bobblehead promotions increase the most attendance and it has the lowest p-value, so I think bobblehead promotions is better than all other promotions.

c. 
```{r message=FALSE}
p1 = ggplot(df5, aes(x=month, y=attend)) + stat_summary(fun.y="sum", geom="bar")
p1
sum(df5[((df5$month == 'JUN'|df5$month == 'JUL'|df5$month == 'AUG') & df5$bobblehead == 'YES'),]$attend)
```
We should order 432135 booblehead for the summer time.